---
title: "DS Course Data"
author: "Syed Muzammil Iqbal"
date: "2022-09-17"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
```


## Importing the data

```{r cars, warning=FALSE,message=FALSE}


ds_course_data = read.csv("Data/Data - DS C1 Course.csv")
```

## Exploratory Data Analysis (EDA)

```{r EDA, echo=FALSE}

```

## Running Python in R

We will demonstrate how python will run in RStudio

```{r}
library("reticulate")
```

Importing libraries

```{python}

import pandas as pd
import numpy as np
import seaborn as sns
import matplotlib.pyplot as plt


ds_course_data = pd.read_csv("Data/Data - DS C1 Course.csv")
ds_course_data.head()

```
Data Cleaning

```{python}
##shape of the data
ds_course_data.shape
```
```{python}
##attributes of the data
ds_course_data.columns

```
```{python}
##information of the data
ds_course_data.info()

```
Missing Values

```{python}
# missing values percentage
missing_values_series=ds_course_data.isnull().sum()
missing_columns=missing_values_series[missing_values_series>0]
missing_columns_df=(missing_columns.sort_values()/ds_course_data.shape[0])*100
x_col="Attributes"
y_col="Missing Pct %"
missing_columns_df=pd.DataFrame(data=np.column_stack([missing_columns_df.index,missing_columns_df.values]),columns=[x_col,y_col])
missing_columns_df

```
### Descriptive Statistics

Do you understand that this is a paid course ?
```{python}


ds_course_data['Do you understand that this is a paid course ?'].describe()

data_ = ds_course_data.groupby('Do you understand that this is a paid course ?')['Do you understand that this is a paid course ?'].count()
data_ = pd.DataFrame({'Do you understand that this is a paid course ?':data_.index, 'Count':data_.values})
plt.pie(data_['Count'],labels = data_['Do you understand that this is a paid course ?'],autopct='%1.1f%%',shadow=True);
plt.title('Do you understand that this is a paid course ?')

```
Gender Analysis
```{python}

data_ = ds_course_data.groupby('Gender')['Gender'].count()
data_ = pd.DataFrame({'Gender':data_.index, 'Count':data_.values})
data_

data_ = ds_course_data.groupby('Gender')['Gender'].count()
data_ = pd.DataFrame({'Gender':data_.index, 'Count':data_.values})
plt.pie(data_['Count'],labels = data_['Gender'],autopct='%1.1f%%',shadow=True);
plt.title('Gender Analysis')
```
Age Distribution
```{python}
data_ = ds_course_data.groupby('Age')['Age'].count()
data_ = pd.DataFrame({'Age':data_.index, 'Count':data_.values})
data_


dfy=ds_course_data.groupby('Age')['Age'].count()
data_age = pd.DataFrame({'Age':dfy.index, 'Count':dfy.values})
df_age=data_age.sort_values('Count', ascending=False)

df_age=df_age.sort_values('Count', ascending=False)
ax=df_age.plot.bar(x='Age', y='Count',figsize=(15, 8), color='#d4403b')
plt.title('Age Distribution', fontsize=14)
plt.xlabel('Age')

total = len(df_age)
for p in ax.patches:
 percentage = '{:.0f}'.format(p.get_height())
 x = p.get_x() + p.get_width()/8
 y = p.get_y() + p.get_height()+0.02
 ax.annotate(percentage, (x, y))
plt.show()

```
How and where did you hear about this course? 
```{python}
data_ = ds_course_data.groupby('How and where did you hear about this course?')['How and where did you hear about this course?'].count()
data_ = pd.DataFrame({'How and where did you hear about this course?':data_.index, 'Count':data_.values})
data_

```
Which Country are you currently residing in?
```{python}
data_ = ds_course_data.groupby('Which Country are you currently residing in?')['Which Country are you currently residing in?'].count()
data_ = pd.DataFrame({'Which Country are you currently residing in?':data_.index, 'Count':data_.values})
data_


order = ds_course_data['Which Country are you currently residing in?'].value_counts(ascending=False).index
ax = sns.countplot(y="Which Country are you currently residing in?", data=ds_course_data, order=order)
plt.title('Which Country are you currently residing in?', fontsize=14)
plt.xlabel('Number of students')
total = len(ds_course_data['Which Country are you currently residing in?'])
for p in ax.patches:
 percentage = '{:.0f}'.format(p.get_width())
 x = p.get_x() + p.get_width() + 0.02
 y = p.get_y() + p.get_height()/2
 ax.annotate(percentage, (x, y))
plt.show()

```
Which City are you currently residing in?
```{python}
data_ = ds_course_data.groupby('Which City are you currently residing in?')['Which City are you currently residing in?'].count()
data_ = pd.DataFrame({'Which City are you currently residing in?':data_.index, 'Count':data_.values})
data_


order = ds_course_data['Which City are you currently residing in?'].value_counts(ascending=False).index
ax = sns.countplot(y="Which City are you currently residing in?", data=ds_course_data, order=order)
plt.title('Which City are you currently residing in?', fontsize=14)
plt.xlabel('Number of students')
total = len(ds_course_data['Which City are you currently residing in?'])
for p in ax.patches:
 percentage = '{:.0f}'.format(p.get_width())
 x = p.get_x() + p.get_width() + 0.02
 y = p.get_y() + p.get_height()/2
 ax.annotate(percentage, (x, y))
plt.show()
```
Are you currently attending University / College?
```{python}
data_ = ds_course_data.groupby('Are you currently attending University / College?')['Are you currently attending University / College?'].count()
data_ = pd.DataFrame({'Are you currently attending University / College?':data_.index, 'Count':data_.values})
data_

data_ = ds_course_data.groupby('Are you currently attending University / College?')['Are you currently attending University / College?'].count()
data_ = pd.DataFrame({'Are you currently attending University / College?':data_.index, 'Count':data_.values})
plt.pie(data_['Count'],labels = data_['Are you currently attending University / College?'],autopct='%1.1f%%',shadow=True);
plt.title('Are you currently attending University / College?')
```
Latest Degree Completed or in Progress?
```{python}
data_ = ds_course_data.groupby('Latest Degree Completed or in Progress?')['Latest Degree Completed or in Progress?'].count()
data_ = pd.DataFrame({'Latest Degree Completed or in Progress?':data_.index, 'Count':data_.values})
data_

```
Name of University or College currently or previously attended?
```{python}
order = ds_course_data['Name of University or College currently or previously attended?'].value_counts(ascending=False).index
ax = sns.countplot(y="Name of University or College currently or previously attended?", data=ds_course_data, order=order)
plt.title('Name of University or College currently or previously attended?', fontsize=14)
plt.xlabel('Number of students')
total = len(ds_course_data['Name of University or College currently or previously attended?'])
for p in ax.patches:
 percentage = '{:.0f}'.format(p.get_width())
 x = p.get_x() + p.get_width() + 0.02
 y = p.get_y() + p.get_height()/2
 ax.annotate(percentage, (x, y))
plt.show()

```
Prior Work Experience in Data Science or Machine Learning
```{python}
data_ = ds_course_data.groupby('Prior Work Experience in Data Science or Machine Learning')['Prior Work Experience in Data Science or Machine Learning'].count()
data_ = pd.DataFrame({'Prior Work Experience in Data Science or Machine Learning':data_.index, 'Count':data_.values})
data_



```